---
title: "R Notebook"
output: html_notebook
---
```{r}
install.packages("sf")
install.packages("rworldmap")
```


```{r}
library(tidyverse)
library(ggplot2)
library(plotly)
library(gganimate)
library(rworldmap)

```

#worldhap-->
#world2020-->


```{r}
world2020
```

```{r}
worldhap
```

#Interactive Geom_col 1(Region:Happiness)
```{r}
m<-ggplot(data= world2020,
mapping= aes(x = world2020$"Regional indicator" , y= world2020$"Ladder score", fill= world2020$"Country name"))+
geom_col() +
theme(axis.text.x = element_text (angle = 90), legend.position = "none")+
labs(x= "Region",y= "Happiness Ranking",
title = "Rankings for Every Region's Happiness Level",
subtitle="Year: 2020",
caption="Source: Kaggle- World Happiness Report 2020")

plot(m)

```

#Interactive Geom_col 2 (Economic:Happiness)
```{r}
ggplot(data = world2020, aes(x = world2020$"Logged GDP per capita" , y = world2020$"Ladder score", fill = world2020$"Regional indicator"))+
geom_point(shape = 1)+
geom_smooth(method= lm, color = "pink")+
theme(axis.text.x = element_text (angle = 30))+
labs(title="Country's Economy vs. Their Happiness",
x= "GDP Per Capita",
y= "Happiness Score",
caption= "Source:Kaggle- World Happiness Report 2020")

ggplotly(p)

```

#Interactive Graph 3 (Corruption: Life Expectancy)
```{r}
p <-ggplot(data= world2020,
mapping= aes(x = world2020$"Regional indicator", y= world2020$"Perceptions of corruption", color = world2020$"Healthy life expectancy"))
p + geom_col() + guides(fill = FALSE)+
theme(axis.text.x = element_text (angle = 90))+
labs(x= "Region",y= "Corruptive Outlook",
title = "Corruption's Effect on Average Life Expectancy",
subtitle="Year: 2020",
caption="Source: Kaggle")
 
```

#Interactive Geom_point 4 (Freedom:Positive Effect)
#Add smoothing
```{r}
p <- ggplot(data = worldhap, aes(x = Freedom , y =worldhap$"Positive affect", fill = worldhap$"Country (region)"))+
geom_point(shape = 1)+
geom_smooth(size = 0.5, method = "loess", se = FALSE)+
theme(legend.position = "none")+
labs(title="Freedom's Positive Effect Worldwide",
x= "Freedom Score",
y= "Positive Affect",
caption= "Source:Kaggle- World Happiness")

ggplotly(p)
```

#Interactive Geom_Point 5(Generosity:Happiness)
```{r}
p <- ggplot(data = world2020, aes(x = Generosity , y =world2020$"Ladder score", fill = world2020$"Country name"))+
geom_point(shape = 1)+
geom_smooth(method= lm, color = "pink")+
theme(legend.position = "none")+
labs(title="Generosity's Effect on Happiness Worldwide",
x= "Generosity Score",
y= "Happiness Score",
caption= "Source:Kaggle- World Happiness Report 2020")

ggplotly(p)
```

#GGAnimate Graph 1 (Social Support:Generosity)
```{r}
ggplot(world2020, aes(Generosity, world2020$"Social support", colour = world2020$"Regional indicator" ))+
geom_point() +
transition_states(
world2020$"Regional indicator",
transition_length = 3,
state_length= 1)+
enter_fade()+
exit_shrink()+
ease_aes('sine-in-out')+
theme(axis.text.x = element_text (angle = 90))+
#Here comes the gganimate code
labs(title="Worldwide Social Support vs. Generosity",
subtitle= "By Region: {closest_state}",
x= " Region's Generosity Score",
y= "Region's Social Support Rate",
caption= "Source: Kaggle- World Happiness 2020")

 
```

#GGAnimate Graph 2 (Discussion Point Plot)
```{r}
ggplot(world2020, aes(world2020$"Ladder score", world2020$"Healthy life expectancy", colour = world2020$"Regional indicator"))+
geom_point(alpha = 0.5)+
transition_states(world2020$"Regional indicator",
transition_length = 2,
state_length= 1)+
scale_size(range = c(2,15))+
scale_x_log10() +
facet_wrap(~world2020$"Regional indicator")+
labs(title="World Happiness vs. Worldly Life Expectancy",
subtitle= "By Region: {closest_state}",
x= "Happiness Score",
y= "Life Expectancy",
caption= "Source: Kaggle- World Happiness 2020")
```


#Map 1 (Top 10 Happiest Countries)
```{r}
library(maptools)
    data=(wrld_simpl)
    myCountries = wrld_simpl@data$NAME %in% c("Finland", "Denmark", "Norway", "Iceland", "Sweden", "Netherlands", "New Zealand", "Switzerland", "Austria", "Canada")
    plot(wrld_simpl, col = c(gray(.80), "yellow")[myCountries+1])
```

#Map 2 (Finland- Happiest Place on Earth)
```{r}
library(maptools)
    data=(wrld_simpl)
    myCountries = wrld_simpl@data$NAME %in% c("Finland")+
        #choose the desired nation(s) you would like to highlight
    plot(wrld_simpl, col = c(gray(.80), "yellow")[myCountries+1])
```

#Plot 10! World Happiness Pie Chart
```{r}
library(plotly)
pie <- plot_ly(world2020, labels = ~world2020$"Regional indicator", values = ~world2020$"Ladder score", type = 'pie')
pie <- pie %>% layout(title = 'World Happiness Composition',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

pie
```



